---
title: "Protein on Egg Viability"
output: 
    rmdformats::readthedown:
      code_folding: hide
      code_download: true
      toc_depth: 4
editor_options: 
  chunk_output_type: console
---
# Setting-up {.tabset}

## Loading packages
```{r}
pacman::p_load(lme4,
               here,
               car,
               tidyverse,
               ggpubr,
               orchaRd,
               metafor,
               patchwork)
```

## Loading data
```{r}
dat <- read.csv(here("Data","Protein_viability_2.csv"))
```

## Sample sizes
```{r}
count(dat, lifestage)
count(dat, parent)
```
# Analysis 

## Calculating lnRR and Variance
``` {r}

# DATASET WITH VARIANCE
dat2 <- dat %>%
  drop_na()

#transforming data

#transforming mean
asin_trans <- function(percent) {asin(sqrt(percent/100)) }
dat2$high_protein_asin <- asin_trans(dat2$high_protein) 
dat2$low_protein_asin <- asin_trans(dat2$low_protein)

#transforming SD
dat2$high_sd_transform <- sqrt((dat2$high_sd/100)^2/(4*(dat2$high_protein/100)*(1-(dat2$high_protein/100))))
dat2$low_sd_transform <- sqrt((dat2$low_sd/100)^2/(4*(dat2$low_protein/100)*(1-(dat2$low_protein/100))))

#lnRR 
dat2$lnRR <- log(dat2$high_protein_asin) - log(dat2$low_protein_asin)

#variance
dat2$var <- (dat2$high_sd_transform)^2/((dat2$n_HP)*(mean(dat2$high_protein_asin)^2)) + (dat2$low_sd_transform)^2/((dat2$n_HP)*(mean(dat2$low_protein_asin)^2))

# DATASET WITHOUT VARIANCE
dat$high_protein_asin <- asin_trans(dat$high_protein) 
dat$low_protein_asin <- asin_trans(dat$low_protein)

dat$lnRR <- log(dat$high_protein_asin) - log(dat$low_protein_asin)

#write.csv(dat2,'processed_data.csv')
```

## Meta-analysis {.tabset}

### MA with variance
```{r}

m1 <- rma.mv(yi = lnRR, V = var, random = list(~1|esID,
                                               ~1|paperID,
                                               ~1|order),
                 test = "t",
                 data = dat2)
summary(m1) 
i2_ml(m1)

orchard<- orchard_plot(m1, mod = "Int", xlab = "lnRR", alpha=0.4) +  # Orchard plot 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5)+ # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2)+ # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  # scale_colour_manual(values = "darkorange")+ # change colours
  # scale_fill_manual(values="darkorange")+ 
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13)) 

orchard
```

### MA with equal variance
```{r}
m2 <- rma.mv(yi = lnRR, V = 1, random = list(~1|esID,
                                            ~1|paperID,
                                            ~1|order),
                 test = "t",
                 data = dat)
summary(m2) 
i2_ml(m2)

orchard2<- orchard_plot(m2, mod = "Int", xlab = "lnRR", alpha=0.4) +  # Orchard plot 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5)+ # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2)+ # confidence intervals
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  # scale_colour_manual(values = "darkorange")+ # change colours
  # scale_fill_manual(values="darkorange")+ 
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
        text = element_text(size = 24), # change font sizes
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 13)) 

orchard2
```

### Figure 1
```{r, fig.width=15, fig.height=7, message=FALSE}
panel1 <- (orchard + orchard2) + plot_annotation(tag_levels = "A")
panel1
```

## Meta-regression {.tabset}
Meta-regression was done using studies for which we could calculate variance

### Sex
```{r}
m3<- rma.mv(yi = lnRR, V = var, mod = ~parent-1, random = list(~1|esID,
                                               ~1|paperID,
                                               ~1|order),
                 test = "t",
                 data = dat2)
summary(m3) 
r2_ml(m3)

orchard3 <- orchard_plot(m3, mod = "parent", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  scale_colour_manual(values = c("grey34","grey34", "grey34")) +
  scale_fill_manual(values=c("grey34","grey34", "grey34")) +
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 

orchard3
```

### lifestage
```{r}
m4 <- rma.mv(yi = lnRR, V = var, mod = ~lifestage-1, random = list(~1|esID,
                                               ~1|paperID,
                                               ~1|order),
                 test = "t",
                 data = dat2)
summary(m4) 
r2_ml(m4)

orchard4 <- orchard_plot(m4, mod = "lifestage", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction intervals
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) + # confidence intervals
  scale_colour_manual(values = c("grey34","grey34")) +
  scale_fill_manual(values=c("grey34","grey34")) +
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       text = element_text(size = 15), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 

orchard4
```

### Figure 2
```{r, fig.width=15, fig.height=7, message=FALSE}
panel2 <- (orchard4 + orchard3) + plot_annotation(tag_levels = "A")
panel2
```


### Figure 3
```{r}
m5 <- rma.mv(yi = lnRR, V = var, mod = ~order-1, random = list(~1|esID,
                                               ~1|paperID),
                 test = "t",
                 data = dat2)

orchard5 <- orchard_plot(m5, mod = "order", xlab = "lnRR", alpha=0.4) + 
  geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR), height = 0, show.legend = FALSE, size = 1.1, alpha = 0.5) + # prediction interval
  scale_colour_manual(values = c("grey34","grey34", "grey34","grey34", "grey34", "grey34", "grey34", "grey34", "grey34")) +
  scale_fill_manual(values=c("grey34","grey34", "grey34","grey34", "grey34", "grey34", "grey34", "grey34", "grey34")) +
  geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL), height = 0.05, show.legend = FALSE, size = 2) +
  geom_point(aes(fill = name),  size = 5, shape = 21)+ # mean estimate
  scale_size_continuous(range = c(1, 7))+ # change point scaling
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1.3), # border around the plot
       text = element_text(size = 10), # change font sizes
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10)) 

orchard5
```

## Publication bias and sensitivity analysis {.tabset}
PB and sensitivity analysis was done using studies for which we could calculate variance

### Funnel plot
```{r}
funnel(m1)
```

### Leave-one-group-out sensitivity analysis
```{r}

dat2<- dat2 %>% mutate(leave_out = paste(first_author, year, sep = "_"))
dat2$leave_out<- as.factor(dat2$leave_out)
dat2$year <- as.integer(dat2$year)

LeaveOneOut_effectsize <- list()
for(i in 1:length(levels(dat2$leave_out)))
    {
  LeaveOneOut_effectsize[[i]] <- rma.mv(yi = lnRR, V = var, 
                                        random = list(~1 | esID,~1| paperID), 
                                        method = "REML", data = dat2[dat2$leave_out != levels(dat2$leave_out)[i], ])
      }


# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(m1){
  df <- data.frame(est = m1$b, lower = m1$ci.lb, upper = m1$ci.ub)
  return(df)
}


#using dplyr to form data frame
MA_CVR <- lapply(LeaveOneOut_effectsize, function(x) est.func(x))%>% bind_rows %>% mutate(left_out = levels(dat2$leave_out))

#telling ggplot to stop reordering factors
 MA_CVR$left_out  <- as.factor(MA_CVR$left_out )
 MA_CVR$left_out <- factor(MA_CVR$left_out,  levels = MA_CVR$left_out)


#plotting
leaveoneout <- ggplot(MA_CVR) +
  geom_hline(yintercept = 0, lty = 2, lwd = 1) +
  geom_hline(yintercept = m1$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = m1$b, lty = 1, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = m1$ci.ub, lty = 3, lwd = 0.75, colour = "black") +
  geom_pointrange(aes(x = left_out, y = est, ymin = lower, ymax = upper)) +
  xlab("Study left out") + 
  ylab("lnRR, 95% CI") + 
  coord_flip() +
  theme(panel.grid.minor = element_blank())+
  theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank() ) +
  theme(axis.text.y = element_text(size = 6))

leaveoneout
```